%---------------------------------
%Basic Geometry, Encoding and Font
%---------------------------------
\documentclass[british,12pt,a4paper]{article}
\usepackage{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\usepackage[left=2.54cm, right=2.54cm, top=2.54cm, bottom=2.54cm]{geometry}
\usepackage{csquotes}
%------------
%Bibliography
%------------
\usepackage[
backend=biber,
style=apa,
natbib=true,
]{biblatex}
\addbibresource{Leadership Article.bib}
%--------------
%Setting Title
%--------------
\title{{\fontsize{14}{15} \textbf{Discharge Medication Education}}}
\author{\vspace{-1em}{\fontsize{14}{15} Student ID's: 289955511, 326609248, 876923194,} \\ {\fontsize{14}{15}902467787, 915365341 and 997283760}}
\date{}
%----------------------
%Section heading style
%----------------------
\usepackage{titlesec}
\titleformat{\section}
{\centering\normalfont\fontsize{14}{15}\bfseries}{\thesection.}{1em}{}
\setcounter{secnumdepth}{0}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{2pt plus 2pt minus 2pt}
\titleformat{\subsection}
{\normalfont\fontsize{14}{15}\bfseries}{\thesection.}{1em}{}
\setcounter{secnumdepth}{0}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{2pt plus 2pt minus 2pt}
\titleformat{\subsubsection}
{\normalfont\fontsize{14}{15}\bfseries\itshape}{\thesection.}{1em}{}
\setcounter{secnumdepth}{0}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{2pt plus 2pt minus 2pt}
%------------
%Header Style
%------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{DISCHARGE MEDICATION EDUCATION}
\fancyhead[R]{}
\fancyfoot{}
\fancyfoot[R]{\thepage}
\setlength{\headheight}{15pt}
\renewcommand{\headrulewidth}{0pt}
%--------------------------------------
%Indenting and Paragrapth justification
%--------------------------------------
\usepackage{setspace}
\usepackage{parskip}
\newlength{\normalparindent}
\setlength{\normalparindent}{\parindent}
\raggedright
\setlength\parskip{5pt}
\setlength\parindent{0.5 in}
\setlength\bibhang{0.5 in}
\usepackage{indentfirst}
\doublespacing
%----------------------------
%Coloring for links and table
%----------------------------
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{multirow}
%-------------
%Table spacing
%-------------
\setlength{\tabcolsep}{10pt}
\renewcommand{\arraystretch}{1.5}
%-------------------------
%Hyperlinks and PDF set up
%-------------------------
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,      
	urlcolor=blue,
	citecolor=black,
	linkcolor=black,
	pdfauthor={Avery Zavoda},
	pdftitle=Nursing,
	pdfsubject=Nursing,
	pdfproducer=Latex with hyperref,
	pdfpagemode=FullScreen,
	pdfcreator=pdfLatex,
}
%--------------
%Begin Document
%--------------
\begin{document}
%--------------------------------
%Print Title and Initiate Heading
%--------------------------------
\maketitle
\thispagestyle{fancy}
%---------
%Main Body
%---------
Medications are an essential part of most medical treatments, particularly during hospitalisation. However, support for patients transitioning from hospitalisation to the community is lacking despite medication errors posing a significant risk to patient health \parencite{Alqenae2020}.

Over placement, nursing students saw the struggles of providing proper medication education to patients. Medication education is essential for nurses to align with the fundamentals of care framework. The fundamentals of care framework aim to address a patient's physical, psychosocial and relational well-being, encompassing a holistic approach to patient care \parencite{Dempsey2013}. The framework's components include relationship building, integration of care, and context of care. Integration of care is a significant component of the fundamentals of the care framework. Medication education is relevant to factors of the framework, such as providing patient education and information. Proper education in nursing care helps address specific patient needs, such as psychosocial needs.

During hospitalisation, most of the medication administration is done by health care professionals, and this leaves patients feeling unprepared for self-medication post-discharge \parencite{Mortelmans2021}. Medication education upon discharge facilitates informed decision-making and empowers individuals to participate actively in their health management. By providing patients with knowledge about their conditions, treatment plans, and self-care strategies, nurses enable them to take ownership of their health and make health-promoting choices. Patient education also fosters patient confidence. When patients know what to expect and feel confident in their understanding of their medications, they are less likely to experience anxiety or stress related to their treatment. Furthermore, educating patients with comprehensive information, including dosage, administration techniques, and potential side effects, reduces the likelihood of medication-related errors post-discharge.

\section{Background}
As experienced by students on placement, the nurse taking the time to explain medication administration and regimes to the patient before discharge benefits patient confidence, self-managing abilities, and adherence to the prescribed medication regimes. For example, a student and RN spoke to a patient before discharge, feeling anxious and stressed by the medications prescribed for them to follow. The student and the RN took the time to explain to the patient and whanau identifying characteristics and the purposes of each medication, when it was required to be taken and how each medication was prescribed in the regime. The patient expressed genuine gratitude to the student and RN for educating and communicating the requirements of their medication regime, stating that as they can comprehend what is required, they feel more competent to identify and adhere to what is needed.

The transition from hospital care to the community poses a significant risk factor for medication-related harm \parencite{Flatman2021}. \textcite{Alqenae2020} found that post-discharge, over 50\% of adult patients encounter medication errors, and nearly 20\% experience an adverse drug event. Medication education before discharge is pivotal in preventing errors by ensuring the patient feels competent in self-administering their medication regime \parencite{Hajialibeigloo2021}. After admission, patients' medication regimes have the potential to change substantially by discharge, requiring readjustment to this new regime \parencite{Weir2020}.

During hospitalisation, nurses are responsible for medication management. Upon discharge, responsibility is transferred to the patient, often with limited external guidance from healthcare professionals. The patient must have the knowledge to safely administer and follow the medication regime post-discharge, including knowing and recognising their medications, their medication schedule, and the ability to administer the correct dose at the proper time \parencite{Mortelmans2021}.

\section{Discussion}
Aiding in the discharge of patients and explaining their discharge summary and medication regime are all part of a nurse's role. \textcite{Sulosaari2014} depicts medication management as one of the fundamental roles of the nurse and the importance of ensuring sufficient medication competence to the patient before discharge. Although other healthcare professionals, such as pharmacists and doctors, are responsible for ensuring that the person getting discharged is educated appropriately, the relationship between the nurse and patient allows for information to be conveyed more comprehensively. The established trusting and interpersonal relationship between the patient and nurse throughout their stay allows the nurse to be the person the patient will go to with questions that the nurse can answer competently. Often, on clinical placements, students have found that the patient may understand what is being explained to them but have further questions later.

\textcite{Phatak2015} found that pharmacist involvement and medication education when discharging a patient decreased the incidence of patients being readmitted to the ward due to relapse or their condition worsening. It was also found that adequately explaining the medication to the patient decreased ED visits. \citeauthor{Phatak2015} states that adverse drug events paired with patients being uneducated about the medications prescribed post-discharge are leading factors in readmission. \citeauthor{Phatak2015} found "that less than 60\% of patients knew the indication for a new medication prescribed at discharge". This shocking statistic shows the worth of taking time to educate the patient. Understanding the role and purpose of the medication gives patients a sense of agency and prevents unnecessary adverse drug reactions.

Similarly,  A meta-analysis by \textcite{Alper2023} found that medication review by the nurse to the patient is likely to reduce hospital readmission by reducing the likelihood of an adverse drug event. This shows the importance of education before discharge, as hospitals are busy environments; the readmission of patients by preventable circumstances adds to the stress of the healthcare professionals and negatively impacts the patient's physical and psychosocial well-being.

\citeauthor{Alper2023} states that medication education "provides an opportunity for clinicians to ensure that patients understand what medications they are taking, how to take them, and why they are taking them". The systematic review evaluates that medication education is associated with a decrease in actual and potential adverse drug events. When a patient leaves the hospital, although it may be the end of their journey with the nurses and healthcare professionals, their medical journey continues for the individual and their whanau. Whether the discharged patient must take medications for the rest of their lives, for only a short period, or as needed, they must get the education to understand their medications to take them safely \parencite{Yap2016}. The time taken to do this should be considered an essential part of patient care \parencite{Flatman2021}.

\section{Conclusion}
Medication education is a critical component within the fundamentals of care framework as it significantly impacts the outcomes and safety of a patient. This interconnects with the framework's holistic approach to patient care, which integrates physical, psychosocial and relational well-being. The transition from hospital to home care poses a high risk of medication-related harm. However, studies indicate that comprehensive patient education during this discharge transition can effectively reduce medication errors and adverse drug events. The role of nurses in medication education is crucial. Nurses educate the patient during discharge by explaining medication regimens and discharge summaries, further developing a trusting relationship with the patient and their caregivers during and after the hospital stay. This relationship with the patient allows the nurse to deliver information comprehensibly and answer any possible questions the patients may have, ensuring they fully understand their medication instructions.

Studies by \citeauthor{Alper2023} and \citeauthor{Phatak2015} focus on the subject of thorough medication education lowering the risk of hospital and emergency department readmissions, which emphasises the importance of medication education in patient care. Including family members and caregivers during education can enhance knowledge, adherence, and confidence in medication administration. As \citeauthor{Alper2023} stated, medication education ensures that patients understand the medication they are administering, how to take it, and why they are taking it. This knowledge is critical for the patient's health journey, as well as their caregivers and whanau, especially after discharge.

Time is another constraint for nurses working in a busy hospital environment. The time allowed for discussions with patients pre-discharge is crucial to their success in the community \parencite{Sanjai2019}. With time, nurses cannot only discuss but also help teach patients how to self-medicate their medications whilst still in the hospital.

Medication education is essential to the fundamentals of care framework, especially for optimising health outcomes, ensuring patient safety and supporting a comfortable transition from hospital to community care. This approach helps the patient's well-being and reduces the burden on healthcare systems by preventing unnecessary readmissions and promoting effective long-term health management.

\section{Recommendations}
When providing recommendations, we want change to align with 'The Fundamentals of Care Framework' \parencite{Dempsey2013} because, as nurses, the trusting relationship we establish with patients is what will aid in us educating a patient well and altering the information given to address their needs. Patients often feel comfortable directing their questions to the nurses involved. Usually, the nurse spends more time with the patient than other health professionals and can accommodate and tailor answers to help the patient understand their medications. Issues around education upon discharge on medication discussed fall towards the medical competency nurses have regarding the medications, how they allow time to discuss information with patients and their families and the systematic way nurses deliver discharge education. If patients can practise self-administering medication with a nurse whom they trust and who can support them psychosocially through encouragement, they can build the confidence to overcome further medical challenges \parencite{Sanjai2019}. Therefore, we recommend that a nurse familiar with the patient and their care carries out discharge medication education.

Concerning medication competency amongst nurses, programmes such as graduate support and education workshops could provide a safety net to those nurses feeling they need more preparation for the new environment they are now working in. \citeauthor{Sulosaari2014} states that there was room for improvement through policy and educational initiatives based on their study of the education provided in nursing schools for medication. Whilst this is for a nursing school level, we recommend that similar initiatives, policies and guidelines be implemented in the workplace and at a postgraduate level, as learning should continue after graduation. Initiatives could be mini workshops nurses can attend each week, which speak to a different medication or aspect of clinical knowledge. Healthcare strives to find new ways to provide care for patients and search for and achieve better health outcomes for patients. Proper medication education on discharge is a small part that could change the success of patients and their conditions long-term within the community. This change would also empower the nurse to feel confident advising on discharge medication and allow the patient consistency in care.

On placement, students saw that patients they observed self-medicating with their preceptor were able to ask questions that might arise at home and have them answered in the safety of the hospital environment by a health professional who was able to guide the patient and provide education in a way that tailored to their understanding which would overall reduce readmission \parencite{Sanjai2019}. We recommend that more time be allowed for nurses to teach patients about their medications. This change has the potential to significantly reduce the number of readmissions, adverse drug events and non-compliance with medication.

Students on placement found that patients expressed that it was helpful and easier to understand and comply with medication when it was explained to them and provided with a physical reminder and explanation. Everyone is different, and we need to remember that to achieve patient-centred care, it not only starts with us building and forming a trusting relationship but also relies on how well we know our patient and whether we can individualise the care we give to their specific needs as they have a right to quality care that considers their individuality \parencite{NZNC2012}. \textcite{Sanjai2019} conducted a study on whether an educational video on medication upon discharge would benefit patients' and nurses' experiences at discharge and understanding and confidence post-discharge. The study concluded that the educational video significantly improved patients' feelings towards preparation for discharge. While this method of education may work for some, we recommend a mixed approach. We would also recommend that flyers or handouts that have all the information written down be given to patients, as due to fear and anxiety around hospitalisation and discharge, patients are likely to forget what has been explained to them \parencite{Roeung2024}. They could include contact numbers for questions they may have, the frequency and times to take medication, do's and don'ts and a brief description of the medication and what it is doing to aid in their recovery or maintenance of their condition. This can act as wrap-around support for a patient so that they can feel well-prepared to manage their medication themselves when discharged.

%---------
%Word count
%---------
\vfill
\begin{center}
	\large Word Count: 2020
\end{center}
%---------
%Print  Bibliography
%---------
\pagebreak
\doublespacing
\printbibliography
\end{document}
